% Mary please write in this file

CIS 9590 is Information Technology Project Design and Management is the  ``Computer Information Systems'' (CIS) capstone project course for the CIS major wherein the students will apply concepts and techniques from prior course work, to design, develop, and create an implementable application for a working information system of an actual business. It also focuses on the design and management of systems to meet the increased need for information within an enterprise. The course exposes students to the fundamentals of IT project management required for the successful implementation of IT-based systems. The course presents tools and technologies for project definition, work breakdown, estimating, planning and scheduling resources as well as monitoring and control of project execution. Students utilize knowledge gained from prior coursework, and work in groups to design and manage an Information Technology project.  During my first semester Spring 2020 teaching with the students using whatever development tools they were familiar, I noticed this to be a problem so with this knowledge I changed the course to require the use of Intel One API.  This did not get implemented until Fall 2021.  I actually taught the course three times before requiring the software tool uniformly changed.  The course was a 3 hour course, first face-to-face.  Then synchronous online only.  In Fall 2021 we changed to 75 minutes in person and online (hybrid).  Students had to self-teach Intel One API with the use of tutorials and buddy system.  The students seemed to have the necessary skills to learn enough of the software to create an implementable application.  This semester, Spring 2023, the students really seemed to lack the coding skills.
